Suppl. Figure 5. Rarefaction curves

### 2022-08-25 reports/01_taxonomy_improved.Rmd

---
title: "Improve Taxonomy Assignment"
editor_options:
  chunk_output_type: console
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: no
---

@@

```{r Load data, message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
library(tidyverse)
library(phyloseq)
library(Biostrings)
})  })  })

@@

```{r SeqID dict, include=FALSE, results='hide'}
########################
# CREATE SEQUENCE ID's #
########################
Seq_ID_key <-seqtab.taxa %>% 
  bind_rows(.id = "Sequencing_run") %>%
  # Get only uniqe sequences by grouping on all taxonomy
  group_by(Sequence,Kingdom,Phylum,Class,Order,Family,Genus,Species) %>%
  #summarize(n()) %>% filter(`n()`>1) %>% .$`n()` %>% sum(.)
  summarise(Reads_per_taxa = sum(Reads),
            Sequencing_run = paste(unique(Sequencing_run), collapse="; "),
            .groups = "drop") %>%
  bind_cols(Seq_ID = c(paste0("Seq_",sprintf("%05.0f", 1:nrow(.))))) %>%
  {. ->> seqtab.taxa.all } %>% 
  select(Seq_ID, Sequence)

>>>>

---
title: "Improve Taxonomy Assignment"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: show
    toc: yes
    toc_float:
      collapsed: no
editor_options:
  chunk_output_type: console
---

@@

```{r Load data, message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
library(tidyverse)
library(phyloseq)
library(Biostrings)
})  })  })

@@

```{r SeqID dict, results='hide'}
########################
# CREATE SEQUENCE ID's #
########################
Seq_ID_key <-seqtab.taxa %>% 
  bind_rows(.id = "Sequencing_run") %>%
  # Get only uniqe sequences by grouping on all taxonomy
  group_by(Sequence,Kingdom,Phylum,Class,Order,Family,Genus,Species) %>%
  #summarize(n()) %>% filter(`n()`>1) %>% .$`n()` %>% sum(.)
  summarise(Reads_per_taxa = sum(Reads),
            Sequencing_run = paste(unique(Sequencing_run), collapse="; "),
            .groups = "drop") %>%
  bind_cols(Seq_ID = c(paste0("Seq_",sprintf("%05.0f", 1:nrow(.))))) %>%
  {. ->> seqtab.taxa.all } %>% 
  select(Seq_ID, Sequence)

### 2022-08-25 reports/manuscript/Figure2.Rmd

---
title: "Figure 2. Bacterial Communities and Function"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  dev=c('pdf', 'png'), dpi=300,
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

```{r Load data, message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(scales)
  library(igraph)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

@@

```{r Figure 2,echo=FALSE, message=FALSE, warning=FALSE, fig.height=8}

@@

```{r Suppl. Table 2., include=FALSE}
#saveRDS( y , "../../../results/Picrust_EdgeR_estimations.rds" )
top <- top %>% as_tibble(rownames="KO Terms")

>>>>

---
title: "Figure 2. Bacterial Communities and Function"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, out_dir, ...) {
    source("../../code/knit_function.R");
    custom_knit(inputFile, "../../lab_book/Figure2/", ...)
    })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results = "hold",
  message    = FALSE,
  warning    = FALSE,
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

```{r Load data, message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(scales)
  library(igraph)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

@@

```{r Figure 2, fig.height=8}

@@

```{r Suppl. Table 2.}
#saveRDS( y , "../../../results/Picrust_EdgeR_estimations.rds" )
top <- top %>% as_tibble(rownames="KO Terms")

### 2022-08-25 reports/manuscript/Figure3.Rmd

---
title: "Figure 3. Tissue Microbiome Abundances"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  dev=c('pdf', 'png'), dpi=300,
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(RColorBrewer)
  # remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

>>>>

---
title: "Figure 3. Tissue Microbiome Abundances"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, out_dir, ...) {
    source("../../code/knit_function.R");
    custom_knit(inputFile, "../../lab_book/Figure3/", ...)
    })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results = "hold",
  message    = FALSE,
  warning    = FALSE,
  fig.width = 6.6929133858,
  fig.path="./Figures/",
  fig.align = "center",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

```{r message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(scales)
  library(RColorBrewer)
  # remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

### 2022-08-25 reports/manuscript/Suppl.Figure5.Rmd

---
title: "Suppl. Figure 5. Rarefaction curves"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(
  fig.path="./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
```

@@

#############
# LODA DATA #
#############
paths_p <- c('../../../data/phyloseq_boston_r1.RDS',   # CVL V3 (2 replicates of one tissue + 27 CVL V2)
             '../../../data/phyloseq_boston_r2.RDS',   # Tissue V3 & CVL V2
             '../../../data/phyloseq_Sthlm.RDS')       # CVL V2, (only v4 region)

@@

```{r rarefaction curves, fig.height=6, fig.width=8, fig.asp=0.75,  include=FALSE}
##################
# FILTER SAMPLES #
##################
# remove controls and duplicates
# Include column keeps replicate samples
# Include_final column removes all replicates and women that don't have trx samples
ps_filt <- map(ps_list, ~ .x %>%
  subset_samples(., Include_final == "yes"))

@@

```{r Suppl.Fig5 Rarefraction_plot, warning=FALSE, echo=FALSE, fig.align="center", fig.height=6, fig.width=8, fig.asp=0.75,}
### A & B
###########################
# RAREFRACTION CURVE PLOT #
###########################
plot <- ggarrange(
          #rare_plot[[1]] + theme(axis.title.x=element_blank(),plot.margin=unit(c(.5,.5,.5,.5),"cm")),
          #rare_plot[[3]] + theme(axis.title.x=element_blank()),
          rare_plot[[4]] + theme(axis.title.x=element_blank(), plot.margin=unit(c(.5,.5,.5,.5),"cm")),
          rare_plot[[6]] + theme(plot.margin=unit(c(.5,.5,.5,.5),"cm")),
          ncol = 1,
          labels = c("a","b","c","d")
          )
print(plot)

>>>>

---
title: "Suppl. Figure 5. Rarefaction curves"
geometry: "left=2cm,right=2cm,top=2cm,bottom=2cm"
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, out_dir, ...) {
    source("../../code/knit_function.R");
    custom_knit(inputFile, "../../lab_book/SupplFigure5/", ...)
    })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.path="./Suppl.Figures/",
  fig.align = "center",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
# setwd("/Users/vilkal/work/Brolidens_work/Projects/broliden_5325/reports/manuscript")
```

@@

#############
# LODA DATA #
#############
paths_p <- c('../../../data/phyloseq_boston_r1.RDS',   # CVL V3 (2 replicates of one tissue + 27 CVL V2)
             '../../../data/phyloseq_boston_r2.RDS',   # Tissue V3 & CVL V2
             '../../../data/phyloseq_Sthlm.RDS'        # CVL V2, (only v4 region)
             )

@@

```{r rarefaction curves, fig.height=6, fig.width=8, fig.asp=0.75}
##################
# FILTER SAMPLES #
##################
# remove controls and duplicates
# Include column keeps replicate samples
# Include_final column removes all replicates and women that don't have trx samples
ps_filt <- map(ps_list, ~ .x %>%
  subset_samples(., Include_final == "yes"))

@@

```{r Suppl.Fig5 Rarefraction_plot, warning=FALSE, fig.height=6, fig.width=8, fig.asp=0.75,}
### A & B
###########################
# RAREFRACTION CURVE PLOT #
###########################
plot <- ggarrange(
          #rare_plot[[1]] + theme(axis.title.x=element_blank(),plot.margin=unit(c(.5,.5,.5,.5),"cm")),
          #rare_plot[[3]] + theme(axis.title.x=element_blank()),
          rare_plot[[4]] + theme(axis.title.x=element_blank(), plot.margin=unit(c(.5,.5,.5,.5),"cm")),
          rare_plot[[6]] + theme(plot.margin=unit(c(.5,.5,.5,.5),"cm")),
          ncol = 1,
          labels = c("a","b","c","d")
          )
print(plot)
